Assessing United States county-level exposure for tropical cyclone impact research

### 2019-07-28 tables/stormseverity.tex
Update storm severity table

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Wed Oct 10 12:11:35 2018
\begin{table}[ht]
\centering
\caption{Summary statistics for exposure metrics considered to assess county-level exposure to
         tropical cyclones. A county exposure represents the exposure of a specific eastern US
         county to a specific tropical cyclone. A county can be exposed to multiple tropical cyclones within
         a year, and a tropical cyclone can create multiple county exposures under a given metric.
         The median and interquartile range of county exposures per tropical cyclone is based on
         the tropical cyclones for which at least one US county was exposed. The years for which
         data are available for each metric are given in Table 1.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{1.75cm}p{3cm}p{4cm}p{4cm}}
  \toprule
Metric & Mean (interquartile range) of county exposures per year & Median (interquartile range) of county exposures per tropical cyclone & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Distance & 433 (224, 503) & 84 (23, 173) & Beryl, 1994 (330) \\ 
  Rain & 401 (152, 553) & 68 (14, 146) & Frances, 2004 (464) \\ 
  Wind & 224 (83, 353) & 34 (8, 80) & Ike, 2008 (355) \\ 
  Flood & 213 (84, 249) & 26 (6, 57) & Ivan, 2004 (317) \\ 
  Tornado & 53 (16, 43) & 7 (2, 16) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Wed Oct 10 12:11:35 2018
\begin{table}[ht]
\centering
\caption{Summary statistics for the number of county tropical cyclone exposures under each metric.     
	 The median and interquartile range of number of county exposures per tropical cyclone are based on
         the tropical cyclones for which at least one US county was exposed. The years for which
         data are available for each metric are given in Table 1.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{1.75cm}p{3cm}p{4cm}p{4cm}}
  \toprule
Metric & Mean (interquartile range) of county exposures per year & Median (interquartile range) of county exposures per tropical cyclone & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Distance & 433 (224, 503) & 84 (23, 173) & Beryl, 1994 (330) \\ 
  Rain & 401 (152, 553) & 68 (14, 146) & Frances, 2004 (464) \\ 
  Wind & 224 (83, 353) & 34 (8, 80) & Ike, 2008 (355) \\ 
  Flood & 213 (84, 249) & 26 (6, 57) & Ivan, 2004 (317) \\ 
  Tornado & 53 (16, 43) & 7 (2, 16) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}
